%------------------------
% Ethan's Résumé Template
% Author: necusjz
% License: CC-BY-4.0
%------------------------
\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{ragged2e}
\usepackage{etoolbox}
\usepackage{tikz}
\input{glyphtounicode}

% font options
\usepackage{newpxtext}
\linespread{1.05}  % palladio needs more leading (space between lines)
\usepackage[T1]{fontenc}

\pagestyle{fancy}
\fancyhf{}  % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
\setlength{\footskip}{5pt}

% sections formatting
\titleformat{\section}{
  \vspace{-2pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule\vspace{-5pt}]

% ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

% custom commands
\newcommand{\cvitem}[1]{
  \item\small{
    {#1\vspace{-2pt}}
  }
}

\newcommand{\cvheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \small#3 & \small #4 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\cvheadingstart}{\begin{itemize}[leftmargin=0in, label={}]}
\newcommand{\cvheadingend}{\end{itemize}}
\newcommand{\cvitemstart}{\begin{itemize}[label=\textopenbullet]\justifying}
\newcommand{\cvitemend}{\end{itemize}\vspace{-5pt}}

\newcommand{\cvskill}[2]{
  \textcolor{black}{\textbf{#1}}\hfill
  \foreach \x in {1,...,5}{%
    \space{\ifnumgreater{\x}{#2}{\color{black!80!white!20}}{\color{black}}\faSquare}}\par%
  \vspace{-2pt}
}

\renewcommand\labelitemii{$\vcenter{\hbox{\footnotesize$\bullet$}}$}

\begin{document}

% contact information
\begin{center}
  {\LARGE\scshape \textbf{\textcolor{RoyalBlue}{Andrew McQuillen}}} \\[6pt]
  {\small
  \faIcon{envelope} \ \href{mailto:atmcquillen@gmail.com}{\textcolor{RoyalBlue}{atmcquillen@gmail.com}}
  \quad | \quad
  \faIcon{phone} \ \textcolor{RoyalBlue}{+44 7788 561831}
  \quad | \quad
  \faIcon{linkedin} \ \href{https://www.linkedin.com/in/andrew-mcquillen-a70115}{\textcolor{RoyalBlue}{linkedin.com/in/andrew-mcquillen-a70115}}
  }
\end{center}

\section{Profile}
\begin{justify}
  Senior Engineer and Tech Lead with 20+ years’ experience delivering scalable 
  enterprise platforms. Expert in Java, AWS, and modern DevOps, with a proven 
  record of shaping architecture, solving complex problems, mentoring teams, 
  and aligning technology with business outcomes. Strong communicator trusted 
  to drive cross-team initiatives and raise engineering standards.
\end{justify}

\section{Professional Experience}
\cvheadingstart
  \cvheading
    {Civica}{Remote - London, UK}
    {Senior Engineer / Tech Lead}{2022 - Present}
  \cvitemstart
    \cvitem{Directed transformation of iCasework team, modernizing practices and mentoring engineers.}
    \cvitem{Owned architecture and technical strategy for Civica’s configurable Case Management platform.}
    \cvitem{Improved delivery speed and quality by establishing CI/CD pipelines and code standards.}
    \cvitem{Partnered with stakeholders to align roadmap with customer and business priorities.}
  \cvitemend

  \cvheading
    {Civica}{Remote - London, UK}
    {Engineer }{2018 - 2022}
  \cvitemstart
    \cvitem{Integrated iCasework into Civica’s product suite post-acquisition.}
    \cvitem{Delivered high-impact features and led successful projects for major clients.}
    \cvitem{Supported pre-sales through technical workshops and presentations.}
  \cvitemend

  \cvheading
    {iCasework}{Remote - London, UK}
    {Lead Integrations Engineer / 3rd Line Support}{2012 - 2018}
  \cvitemstart
    \cvitem{Drove platform integrations for all client implementations.}
    \cvitem{Key team member contributing to growing company for successful acquisition.}
    \cvitem{Delivered technical workshops and client-facing solution demos.}
  \cvitemend

  \cvheading
    {Tagish}{Alnwick, UK}
    {Analyst Programmer / Consultant}{2003 - 2012}
  \cvitemstart
    \cvitem{Engineered CMS and case management solutions for UK local government.}
    \cvitem{Led deployments across Europe, ensuring successful client adoption.}
  \cvitemend
\cvheadingend

\section{Early Career}
\begin{justify}
1999-2003 - Web Developer / Junior Engineer roles at several UK / Australian companies.
Built foundational technical skills and client-facing experience.
\end{justify}

\section{Education}
\cvheadingstart
  \cvheading
    {University of East Anglia}{Norwich, UK}
    {BSc, Environmental Science}{1996 - 1999}
  \cvheading
    {Coquet High School}{Amble, UK}
    {3 A Levels}{1994 - 1996}
\cvheadingend

\section{Skills}
Java · AWS · Terraform · CI/CD · Docker · Tomcat · PostgreSQL · JUnit · Git · AirByte · 
System Architecture · Agile · Mentoring · Team Leadership · GitHub · ADO  · 
Stakeholder Communication · Strategic Thinking · Continuous Improvement

\section{Misc.}
\cvheadingstart
\item
\cvitemstart
  \cvitem{3x Great North Run finisher for Stroke Association}
  \cvitem{Ran Cinema nights at Archibald First School during my children's time there}
  \cvitem{Volunteer wildlife researcher at Bookmark Biosphere Reserve, Renmark, SA - 2002}
  \cvitem{Travel - Aus, NZ, Thailand, Europe, Africa}
  \cvitem{Enjoy running, football, mountaineering, hiking, camping, cooking, reading and spending quality time with my family}
\cvitemend
\cvheadingend

\end{document}
